---
title: "Aggression in Wintering White-Throated Sparrows"
author: "Daniel Redwine"
output:
  html_document:
    toc: true # table of content true
    toc_float:
      collapsed: true
    toc_depth: 2  # upto three depths of headings (specified by #, ## and ###)
    number_sections: false  ## if you want number sections at each table header
    theme: flatly  # many options for theme, this one is my favorite.
---
```{r packages, message=FALSE, warning=FALSE, echo=FALSE}

library(tidyverse)
library(lme4)
library(lmerTest)
library(ggfortify)
library(MuMIn)
library(asbio)
library(GGally)
library(performance)
library(patchwork)
library(olsrr)
```

# Introduction

The White-throated Sparrow (<i>Zonotrichia albicollis</i>) is a migratory passerine often used as a behavioral model because of the unique mating system involving disassortative pairing of white-stripe and tan-stripe morphs. White-stripe individuals of both sexes are typically characterized as more aggressive than their tan-stripe counterparts during the breeding season. However, few behavioral correlates associated with morph have been identified in the nonbreeding season. We recorded agonistic interactions of color-banded White-throated Sparrows of known sex, age, and morph to assess correlates of occurrence and frequency of agonistic interactions for both aggressors and targets of aggression.

```{r load and clean datasets, message=FALSE, warning=FALSE, echo=FALSE}
# Load in the dataset
total_data <- read.csv("../data/total_data.csv")
agonistic_analysis_data <- read.csv("../data/agonistic_analysis_data.csv")
resight_analysis_data <- read.csv("../data/resight_analysis_data.csv")

# force into numerics and factors just to make sure everything works
total_data$SampleID <- as.factor(total_data$SampleID)
total_data$PCRsex <- as.factor(total_data$PCRsex)
total_data$PCRMorph <- as.factor(total_data$PCRMorph)
total_data$Winter <- as.factor(total_data$Winter)
total_data$Wing <- as.numeric(total_data$Wing)
total_data$Feeding_Density <- as.numeric(total_data$Feeding_Density)
total_data$Platform_Time <- as.numeric(total_data$Platform_Time)
total_data$Aggressor_Occurrence <- as.numeric(total_data$Aggressor_Occurrence)

target_nonzero_data <- total_data %>%
  filter(Total_Recipient != 0)

aggressor_nonzero_data <- total_data %>%
  filter(Total_Agonistic != 0)
```

# Population Demographics

Agonistic interactions of White-throated Sparrows at feeding platforms were recorded from January 1 to March 15 of 2023 and 2024. To obtain demographics of the population at study sites, all individuals resighted and banded during the study period were included. To obtain the subset of the population sampled for agonistic analyses, all individuals in the dataset for agonistic analyses were included. To examine sampling bias, all observations in the datset for agonistic analyses were included which includes repeated measures of individuals. 

```{r population data, message=FALSE, warning=FALSE, echo=FALSE}

```

